Formation of $\cenn$ Molecules in Oxygen-rich Interiors of Type II Supernovae

### 2013-04-01 doc/submit/ms.tex
Modify text for RefReport2.

\documentclass[manuscript]{aastex}

@@

\begin{document}

@@

\author{Tianhong Yu, Bradley S. Meyer, and Donald D. Clayton}
\affil{Department of Physics and Astronomy, Clemson University, Clemson, SC 29634-0978}

@@

Because our goal is to study the chemistry, we can take a very simple physical
model of the expansion; namely, temperature
$T = 3800 K / (t / 100 {\rm d}) =
3.30 \times 10^{10} / t({\rm s})\ {\rm K}$,
where t is the time elapsed since core collapse.
We chooose $n_O = 10^{10}$ cm$^{-3}$
and $n_C = 10^9$ cm$^{-3}$
at the starting time $t = t(6000 {\rm K})$ 
at $T=6000$ K for our chemical network . From our model choice for $T(t)$ we get
$t(6000K) = 5.47 \times 10^6$s. At
subsequent times $n_O(t) = 10^{10}{\rm cm}^{-3}(t/t(6000 {\rm K}))^{-3}$
owing to homologous expansion.
Let $N$ be the number of any specific molecular species
in a comoving, expanding, initially 1 cm$^3$ volume at 6000 K.
The only change of $N$ during
expansion occurs through chemical reactions. $N$ may be expressed as atom
fraction $Y$ of the initial total number
$N_O + N_C = 1.10 \times 10^{10}$ atoms. We
intentionally choose an O-rich interior having $N_O/N_C = 10$,
so that no carbon at
all would be able to condense if that interior were governed by chemical
equilibrium.

@@

The interior core of C and O resulting from completed He burning in massive
stars is a mix of C and O atoms having bulk C/O $<$ 1. Post explosive cooling of
such matter will attempt to associate C and O into CO molecules, with rate
coefficient $k_{CO} = 3.3 \times 10^{-17}$ cm$^3$ s$^{-1}$
\citep{1990ApJ...358..262L}.
The reaction \cotoco\ is one of the crucial reactions of chemical
astrophysics. Its rate $k_{CO}$ is intrinsically slow because quantum mechanics
requires not only rearrangement of electronic shells but also simultaneous
creation of a photon during the collision; nonetheless, the huge product
$n_C n_O$ in the He-exhausted core ensures steady growth for the CO abundance
until it is reversed by radioactive dissociation.

@@

Expressed instead in terms of number fractions $Y_{CO} = n_{CO} / n$
and $Y_C = n_C / n$ where $n$ is the number density of all atoms,
Eq. (\ref{eq:dncodt}) transforms to 
\begin{equation}
\frac{dY_{CO}}{dt} = Y_C Y_O n k_{CO} - \frac{Y_{CO}}{\tau_{CO}}	
\label{eq:dycodt}
\end{equation}
which is the form integrated by our network of coupled reactions.
The number density $n$ is needed for the rate
$n({\rm cm}^{-3}) k_{CO}({\rm cm}^3{\rm s}^{-1})$.
In our numerical example we take $n_O = 10^{10}$ cm$^{-3}$ and
$n_C = 10^9$ cm$^{-3}$ at $t(6000 {\rm K})$ as starting conditions for the
chemical network. Subsequent values are $n = 1.1 \times 10^{10}$ cm$^{-3}$
$[t(6000 {\rm K})/t]^3$, where the expansion factor reduces the initial number
density appropriately. Expansion factors are also in Table 1. Then
Eq. (\ref{eq:comax}) reads:
\begin{equation}
Y_{CO}(t_{max}) = Y_C Y_O n k_{CO} \tau_{CO}
\label{eq:ycomax}
\end{equation}
which is valid during expansions.

@@

Figure \ref{fig:nco}
compares our network calculation of the abundance of CO molecules
with the expectation of Eq. (\ref{eq:comax}) with $\tau_{CO} = \tau_\gamma$
dominating the destruction of CO.
Solid points display the equilibrium product $\ncogeq$ calculated from the
factors shown in Table \ref{tab:quantities}
and from the number densities $n_C$ and $n_O$ after
their initial values at $T=6000$ K have been reduced by the expansion factor
$(t/t(6000 {\rm K}))^{-3}$.
Tight agreement for $T > 4000$ K is immediately evident,
demonstrating that for $T > 4000$ K the abundance of CO is almost exactly in
thermal equilibrium. Eq. (\ref{eq:comax}) validly describes the black dots in
Fig. \ref{fig:nco} because creation and destruction terms are very nearly
balanced while $T > 4000$ K.
Below 3500 K the abundance of CO becomes much smaller than
the expectation $\ncogeq$ of thermal equilibrium because the dissociation of CO
comes to be dominated by Compton electrons. The dashed vertical line at
$T=3500$ K marks the approximate boundary between these two mechanisms for CO
dissociation. Notice carefully in Fig. \ref{fig:nco}
that $n_{CO}$ grows slowly as $T$ falls, not reaching
its final maximum until expansion has cooled to $T=3500$ K.
Although it is obvious that equilbrium CO increases as $T$ falls,
assuming that to occur begs the question of achieving equilibrium.
Our kinetic results demonstrate that CO does quickly achieve its
equilibrium abundance above $T = 4000$ K, and Eq. (\ref{eq:dycodt})
shows that equilibrium to increase as $\tau_\gamma$ lengthens.
At its final maximum $n_{CO} = 1.5 \times 10^6$ cm$^{-3}$,
corresponding to $Y(CO) = 0.7 \times 10^{-3}$. The slow growth of $n_{CO}$
shown in Fig. \ref{fig:nco} differs markedly from the results of
\citet{2009ApJ...703..642C}.
Their results (e.g. Fig. 11) show $n_{CO}$ climbing quickly near 6000 K
to a large
maximum number fraction near 0.1. That maximum would almost exhaust free
carbon. Our results in Fig. \ref{fig:nco}
so differ from theirs that the difference
must be resolved. \citet{2013ApJ...762....5C} has analyzed the expectation
of growth of $n_{CO}$ to a single maximum before declining, and our results are
in line with that expectation.

@@

Figure \ref{fig:yi}
shows the abundances $Y_i$ of each species in our small network as a
function of time $t-t(6000 {\rm K})$ after $T=6000$ K.
From Table \ref{tab:quantities},
start time is $t(6000K) =5.47 \times 10^6$ s.
To display each $Y_i$ on a figure with
reasonable ordinate resolution, we have scaled each $Y_n$\ by the factor
stated in the box. Many features are noteworthy: (1) $Y_C$ and $Y_O$ 
are constant
because their small depletion is negligible on the scale shown;
(2) maxima of $Y_{CO}$ and $Y_2$\ occur at almost exactly the same time
$t-t(6000K)= 4 \times 10^6$ s, as was also seen in Fig. \ref{fig:ncoc2};
(3) $\cthree$\ has very small abundance, about $10^{-7}$ of $Y_2$, 
although much later $Y_3$\ slowly grows modestly
relative to much more abundant $\ctwo$; (4) the rise shapes of $Y_4$
through $Y_8$\ are very similar because they are linked by a near steady
state; (5) the ringed carbon $Y(\ceightr$) has similar abundance shape vs. time,
but notice that it is actually much more abundant than lineaer $C_{7-8}$ and
because it accumulates from isomeric transitions of $\ceight$\
and unlike $\cenn$\ does not
suffer from fast oxidation \citep{1999Sci...283.1290C}. Each of these
features is understandable in terms of the flows into and out of each species.

One sees from Fig. \ref{fig:yi} that the \coctoctwo\ reaction plays no
role in $\ceightr$\ production from the fact that $\ceightr$\ rises only for
$t - t(6000 {\rm K}) > 1.5 \times 10^7$ s, corresponding to $T < 2000$ K,
despite $\ctwo$\ and $\cthree$\ rising at much earlier times.
Whatsoever $\ctwo$\ is made earlier plays no role in $\ceightr$\ production
because the ejection of C atoms from $\cenn$\ at higher $T$ prevents the
flow to $\ceight$.  Only at $T < 2000$ K do those photodissociation reactions
become so slow that $\ceight$\ can grow, which it does from the $\ctwo$\
recently
formed by the \twoctoctwo\ reaction near 2000 K.  Fig. \ref{fig:yi} also shows
that $Y(\ceightr)$
grows quickly to $10^{-16}$.  Since available C is $Y_C = 0.1$,
the ratio gives $10^{-15}$ C/ring.  This is enough to grow very large
graphite.

Figure \ref{fig:cn} shows the shape of $\cenn$\ vs. $n$ for $\cthree$\ to
$\ceight$\ at two different temperatures near 2000 K. As temperature declines,
the curve flattens because photoejection from $\cenn$\ by thermal photons
(or vibrations) weakens. These abundance ratios are almost in a steady state,
but that steady state changes slightly as $T$ falls. These patterns show
almost equal values for $Y(\cthree)$ because that curve is relatively flat
with time near $t-t(6000K) = 10^7$ s (Fig. \ref{fig:yi}).
Table \ref{tab:flows} lists our computed reaction flows both in and out of
$\csix$\ at $T = 2031$ K and $T = 1802$ K.
The reactions are specified there in the
compact notation target(in,out)residual. 
We tabulate the flow magnitudes for $\csix$ to aid readers checking our
numerical results. Fig. \ref{fig:cn} and
Table \ref{tab:flows} are made to be studied together.
Note that the abundances of $\ceight$\ are very small:
$Y(\ceight)= 10^{-36}$ at $T = 1802$ K.
The isomeric transition from linear to
ringed $\ceight$, for which we estimate a lifetime $\tau = 10$ s,
provides the nucleations for graphite growth.

We call attention to several conclusions to be drawn from Table \ref{tab:flows}.
Firstly, the strongest flows by a wide margin involving $\csix$\ are
\cfivectocsix,
which is very fast ($k = 3 \times 10^{-10} {\rm cm}^3 {\rm s}^{-1}$)
because vibrational excitation of $\csix$
obviates the need for creating a photon \citep{1999Sci...283.1290C},
and its inverse reaction which ejects a C atom. Furthermore, those two flows
are equal to each other to three significant figures, illustrating the near 
steady
state of the abundance pattern. Secondly, thermal dissociation of $\csix$\ is
very much faster than its oxidation, showing the small effect of oxidation
on the abundance pattern. The destroying flows from $\csix$\ to $\cfive$
stand in the approximate ratio
${\rm C}_6(\gamma,{\rm C})/{\rm C_6}({\rm O},{\rm CO}) = 5 \times 10^5$
at $T = 2031$ K and $2 \times 10^4$ at $T = 1802$ K.
Dissociation by thermally excited vibrations dominates oxidation. What we here
label ($\gamma,{\rm C}$) is actually radiationless. Note that oxidation of
$\cenn$ molecules is not faster than C-ejection reactions. This unusual
situation occurs because the C-capture reactions proceed by exciting 
vibrations of the $\csix$ molecule. That residual vibrational energy makes
capture reactions fast rather than slow, but also makes the inverse C-ejection
reactions caused by thermally excited vibrations to be much faster. Detailed
balance gets the ratio right. The smaller value for that ratio at $T=1802$ K
occurs because oxidation maintains its effectiveness as $T$ drops but
thermal disruption does not, being much more temperature sensitive.
For this reason the abundance pattern is flatter and $\csix$\ is approximately
3000 times more abundant at $T=1802$ K than at $T=2031$ K.
It is for that reason that destruction flows in Table \ref{tab:flows}
for $\csix$\ are
larger at the smaller temperature.
The steady state shifts to new ratios as $T$ falls.
Thirdly, calculation of the rates will be illustrated for sake of clarity
by the flow
\csixotococfive.
From Fig. \ref{fig:cn}
one sees that at $T = 2031$ K the abundance $Y(\csix) = 10^{-33.3}$.
The value of $Y(O) = 10^{10} cm^{-3} / 1.1 \times 10^{10} cm^{-3} = 0.909$,
so the flow per atom per
second (e.g., Eq. \ref{eq:dycodt}) is
$dY/dt= Y(\csix)Y(O)n(2031K)k(\csix + {\rm O})$.
Expansion from $T=6000$ K to $T=2031$ K has diluted the total number
density $n$ to $1.1 \times 10^{10}{\rm cm}^{-3}
(2031 {\rm K}/6000 {\rm K})^3 = 4.27 \times 10^8{\rm cm}^{-3}$.
The fast oxidation reaction rate factor is
$k(\csix + {\rm O}) = 3 \times 10^{-10} {\rm cm}^3{\rm s}^{-1}$.
Gathering factors yields approximately $4 \times 10^{-35}$ per atom
per second
in good approximation to the Table \ref{tab:flows}
flow entry $3.61 \times 10^{-35}$ per atom per second.

@@

\item Instead of growing large CO abundance near $Y(CO)=0.1$ at $T=5500$ K
as in Fig. 11 of \citet{2009ApJ...703..642C}, we find that $Y(CO)$
builds to a maximum of only $10^{-3}$, which it achieves only slowly
(Fig. \ref{fig:ncoc2}), reaching that maximum only at $T=3500$ K rather
than 5500 K.

@@

\end{enumerate}
We reason that these big differences can be understood if
\citet{2009ApJ...703..642C} had inadvertantly omitted the thermal
dissociation rates of small carbon molecules. Believing that to be the
cause for the discrepancy, we tested that hypothesis by performing our
own trial calculation involving only C, O, CO, $\ctwo$, and $\cthree$,
as they had done,
and omitted the $\tau_\gamma$ destruction terms and the oxidation of $\cthree$.
Figure \ref{fig:no_gamma} displays the result.
The rapid rise of $Y(CO)$ to about $10^{-2}$ at high temperature is very 
similar to Fig. 11 of \citet{2009ApJ...703..642C}.
Similar also is $Y(\ctwo)$,
which grows quickly (Fig. \ref{fig:no_gamma}) to $2 \times 10^{-4}$ of $Y(CO)$,
whereas our Fig. \ref{fig:ncoc2} shows the true value of $Y(CO)$ to be
only $10^{-8}$ at $T=5500$ K and, considerably later,
$Y(\ctwo)/Y(CO) = 10^{-7}$ at their maxima.

With photodissociation turned off, the destruction of $\ctwo$\ occurs primarily
by oxidation, \ctowotococ, whereas production of $\ctwo$ is by
\coctoctwo, the reaction we study in this work.
Those reactions strive to balance, which if achieved would
establish a steady state
ratio $Y(CO)/Y(\ctwo) = 3.5 \times 10^4$. Fig. \ref{fig:no_gamma}
and their Fig. 11 do show
approximately that value, but $Y(\ctwo)$ declines faster than $Y(CO)$
because of declining production of $\ctwo$\ as T declines.

@@

\begin{figure}
\plotone{ncoeq}
\caption{
Comparison of the density of CO molecules calculated by the numerical
network (curve) with the expectation $\ncogeq = n_C n_O k_{CO} \tau_\gamma$
for an abundance
$n_{CO}$ in thermal equilibrium (dots) with photons.
Above T=4000K the CO abundance is seen to be in an accurate thermal
equilibrium, but at lower temperature $n_{CO}$ is increasingly smaller than
thermal equilibrium would require. Instead of thermal photons,
the destruction of CO becomes increasingly dominated by
Compton electrons for $T < 3500$ K.
One see in Fig. \ref{fig:nco} that $n_{CO}$max occurs near 3500K,
which occurs near $10^7$ s (see Table \ref{tab:quantities}).} 
\label{fig:nco}
\end{figure}

@@

\begin{figure}
\plotone{Yi}
\caption{
The abundance (number per atom) of linear chains $\cenn$\ and of ringed isomer
$\ceightr$. We have scaled each $Y(C_n)$ by the factor stated in the box.}
\label{fig:yi}
\end{figure}

@@

\begin{figure}
\plotone{cn}
\caption{
Shape of $Y(C_n)$ vs. n for $\cthree$\ to $\ceight$
at two different temperatures
near 2000K. These shapes can be understood by the relative magnitudes of
flows into and out of $\cenn$.
}
\label{fig:cn}
\end{figure}

@@

\begin{figure}
\plotone{no_gamma}
\caption{
Abundances for network containing only C, O, CO, $\ctwo$, and $\cthree$
when photodissociation of molecules is omitted. Rapid rise of $Y(CO)$
to $10^{-2}$ near 5500 K and the ratio $Y(CO)/Y(\ctwo)$ near $10^4$ are
similar to Fig. 11 of \citet{2009ApJ...703..642C}.
}
\label{fig:no_gamma}
\end{figure}

@@

\begin{table}
\begin{center}
\caption{Values of $\tau_\gamma$(CO) and related quantities at
selected time $t$ and temperature $T$}
\label{tab:quantities}
\begin{tabular}{ccccccc}
\tableline\tableline
$t$ (s) & $\left[t / t(6000 {\rm K}) \right]^{-3}$ & $T$ (K) & $\tau_\gamma$ (s) & $k_{CO}$ (cm$^{-3}$ s$^{-1}$) & $\ncogeq$ (cm$^{-3}$) \\
\tableline
$5.47 \times 10^6$ &
  1 &
  6000 &
  $4.22 \times 10^{-2}$ &
  $3.13 \times 10^{-17}$ &
  $1.32 \times 10^1$ \\
$5.97 \times 10^6$ &
  0.769 &
  5500 &
  $3.54 \times 10^{-1}$ &
  $2.99 \times 10^{-17}$ &
  $6.27 \times 10^1$ \\
$6.57 \times 10^6$ &
  0.578 &
  5000 &
  $4.46 \times 10^{0}$ &
  $2.83 \times 10^{-17}$ &
  $4.24 \times 10^2$ \\
$7.30 \times 10^6$ &
  0.422 &
  4500 &
  $9.70 \times 10^{1}$ &
  $2.67 \times 10^{-17}$ &
  $4.61 \times 10^3$ \\
$8.21 \times 10^6$ &
  0.296 &
  4000 &
  $4.43 \times 10^{3}$ &
  $2.48 \times 10^{-17}$ &
  $9.67 \times 10^4$ \\
$9.38 \times 10^6$ &
  0.198 &
  3500 &
  $5.86 \times 10^{5}$ &
  $2.28 \times 10^{-17}$ &
  $5.26 \times 10^6$ \\
$1.09 \times 10^7$ &
  0.125 &
  3000 &
  $3.77 \times 10^{8}$ &
  $2.05 \times 10^{-17}$ &
  $1.21 \times 10^9$ \\
\tableline
\end{tabular}
\end{center}
\end{table}

@@

\end{document}

>>>>

\documentclass[manuscript]{aastex}
\usepackage{CJK}

@@

\begin{document}
\begin{CJK*}{UTF8}{gbsn}

@@

\author{Tianhong Yu (喻天弘), Bradley S. Meyer, and Donald D. Clayton}
\affil{Department of Physics and Astronomy, Clemson University, Clemson, SC 29634-0978}

@@

Because our goal is to study the chemistry, we can take a very simple physical
model of the expansion; namely, temperature
$T = 3800 K / (t / 100 {\rm d}) =
3.30 \times 10^{10} / t({\rm s})\ {\rm K}$,
where t is the time elapsed since core collapse.
We chooose $n_O = 10^{10}$ cm$^{-3}$
and $n_C = 10^9$ cm$^{-3}$
at the starting time $t = t_{6000 {\rm K} }$ 
at $T=6000$ K for our chemical network . From our model choice for $T(t)$ we get
$t_{6000 {\rm K} } = 5.47 \times 10^6$s. At
subsequent times $n_O(t) = 10^{10}{\rm cm}^{-3}(t/t_{6000 {\rm K}})^{-3}$
owing to homologous expansion.
Let $N$ be the number of any specific molecular species
in a comoving, expanding, initially 1 cm$^3$ volume at 6000 K.
The only change of $N$ during
expansion occurs through chemical reactions. $N$ may be expressed as atom
fraction $Y$ of the initial total number
$N_O + N_C = 1.10 \times 10^{10}$ atoms. We
intentionally choose an O-rich interior having $N_O/N_C = 10$,
so that no carbon at
all would be able to condense if that interior were governed by chemical
equilibrium.

@@

The interior core of C and O resulting from completed He burning in massive
stars is a mix of C and O atoms having bulk C/O $<$ 1. Post explosive cooling of
such matter will attempt to associate C and O into CO molecules 
\citep{1990ApJ...358..262L}.
The reaction \cotoco\ is one of the crucial reactions of chemical
astrophysics. Its rate $k_{CO}$ is intrinsically slow because quantum mechanics
requires not only rearrangement of electronic shells but also simultaneous
creation of a photon during the collision; nonetheless, the huge product
$n_C n_O$ in the He-exhausted core ensures steady growth for the CO abundance
until it is reversed by radioactive dissociation.

@@

Expressed instead in terms of number fractions $Y_{CO} = n_{CO} / n$
and $Y_C = n_C / n$ where $n$ is the number density of all atoms,
Eq. (\ref{eq:dncodt}) transforms to 
\begin{equation}
\frac{dY_{CO}}{dt} = Y_C Y_O n k_{CO} - \frac{Y_{CO}}{\tau_{CO}}	
\label{eq:dycodt}
\end{equation}
which is the form integrated by our network of coupled reactions.
The number density $n$ is needed for the rate
$n({\rm cm}^{-3}) k_{CO}({\rm cm}^3{\rm s}^{-1})$.
In our numerical example we take $n_O = 10^{10}$ cm$^{-3}$ and
$n_C = 10^9$ cm$^{-3}$ at $t_{6000 {\rm K}}$ as starting conditions for the
chemical network. Subsequent values are $n = 1.1 \times 10^{10}$ cm$^{-3}$
$[t_{6000 {\rm K}}/t]^3$, where the expansion factor reduces the initial number
density appropriately. Expansion factors are also in Table 1. Then
Eq. (\ref{eq:comax}) reads:
\begin{equation}
Y_{CO}(t_{max}) = Y_C Y_O n k_{CO} \tau_{CO}
\label{eq:ycomax}
\end{equation}
which is valid during expansions.

@@

Figure \ref{fig:nco}
compares our network calculation of the abundance of CO molecules
with the expectation of Eq. (\ref{eq:comax}) with $\tau_{CO} = \tau_\gamma$
dominating the destruction of CO.
Solid points display the equilibrium product $\ncogeq$ calculated from the
factors shown in Table \ref{tab:quantities}
and from the number densities $n_C$ and $n_O$ after
their initial values at $T=6000$ K have been reduced by the expansion factor
$(t/t_{6000 {\rm K}})^{-3}$.
Tight agreement for $T > 4000$ K is immediately evident,
demonstrating that for $T > 4000$ K the abundance of CO is almost exactly in
thermal equilibrium. Eq. (\ref{eq:comax}) validly describes the black dots in
Fig. \ref{fig:nco} because creation and destruction terms are very nearly
balanced while $T > 4000$ K.
Below 3500 K the abundance of CO becomes much smaller than
the expectation $\ncogeq$ of thermal equilibrium because the dissociation of CO
comes to be dominated by Compton electrons. The dashed vertical line at
$T=3500$ K marks the approximate boundary between these two mechanisms for CO
dissociation. Notice carefully in Fig. \ref{fig:nco}
that $n_{CO}$ grows slowly as $T$ falls, not reaching
its final maximum until expansion has cooled to $T=3500$ K.
Although it is obvious that equilbrium CO increases as $T$ falls,
assuming that to occur begs the question of achieving equilibrium.
Our kinetic results demonstrate that CO does quickly achieve its
equilibrium abundance above $T = 4000$ K, and Eq. (\ref{eq:dycodt})
shows that equilibrium to increase as $\tau_\gamma$ lengthens.
At its final maximum $n_{CO} = 1.5 \times 10^6$ cm$^{-3}$,
corresponding to $Y_{CO} = 0.7 \times 10^{-3}$. The slow growth of $n_{CO}$
shown in Fig. \ref{fig:nco} differs markedly from the results of
\citet{2009ApJ...703..642C}.
Their results (e.g. Fig. 11) show $n_{CO}$ climbing quickly near 6000 K
to a large
maximum number fraction near 0.1. That maximum would almost exhaust free
carbon. Our results in Fig. \ref{fig:nco}
so differ from theirs that the difference
must be resolved. \citet{2013ApJ...762....5C} has analyzed the expectation
of growth of $n_{CO}$ to a single maximum before declining, and our results are
in line with that expectation.

@@

Figure \ref{fig:yi}
shows the abundances $Y_i$ of each species in our small network as a
function of time $t-t_{6000 {\rm K}}$ after $T=6000$ K.
From Table \ref{tab:quantities},
start time is $t_{6000 {\rm K}} =5.47 \times 10^6$ s.
To display each $Y_i$ on a figure with
reasonable ordinate resolution, we have scaled each $Y_n$\ by the factor
stated in the box. Many features are noteworthy: (1) $Y_C$ and $Y_O$ 
are constant
because their small depletion is negligible on the scale shown;
(2) maxima of $Y_{CO}$ and $Y_2$\ occur at almost exactly the same time
$t-t_{6000K}= 4 \times 10^6$ s, as was also seen in Fig. \ref{fig:ncoc2};
(3) $\cthree$\ has very small abundance, about $10^{-7}$ of $Y_2$, 
although much later $Y_3$\ slowly grows modestly
relative to much more abundant $\ctwo$; (4) the rise shapes of $Y_4$
through $Y_8$\ are very similar because they are linked by a near steady
state; (5) the ringed carbon abundance $Y_8^r$ has similar abundance shape 
vs. time,
but notice that it is actually much more abundant than lineaer $C_{7-8}$ and
because it accumulates from isomeric transitions of $\ceight$\
and unlike $\cenn$\ does not
suffer from fast oxidation \citep{1999Sci...283.1290C}. Each of these
features is understandable in terms of the flows into and out of each species.

One sees from Fig. \ref{fig:yi} that the \coctoctwo\ reaction plays no
role in $\ceightr$\ production from the fact that $\ceightr$\ rises only for
$t - t_{6000 {\rm K}} > 1.5 \times 10^7$ s, corresponding to $T < 2000$ K,
despite $\ctwo$\ and $\cthree$\ rising at much earlier times.
Whatsoever $\ctwo$\ is made earlier plays no role in $\ceightr$\ production
because the ejection of C atoms from $\cenn$\ at higher $T$ prevents the
flow to $\ceight$.  Only at $T < 2000$ K do those photodissociation reactions
become so slow that $\ceight$\ can grow, which it does from the $\ctwo$\
recently
formed by the \twoctoctwo\ reaction near 2000 K.  Fig. \ref{fig:yi} also shows
that $Y_8^r$
grows quickly to $10^{-16}$.  Since available C is $Y_C = 0.1$,
the ratio gives $10^{15}$ C/ring.  This is enough to grow very large
graphite.

Figure \ref{fig:cn} shows the shape of $\cenn$\ vs. $n$ for $\cthree$\ to
$\ceight$\ at two different temperatures near 2000 K. As temperature declines,
the curve flattens because photoejection from $\cenn$\ by thermal photons
(or vibrations) weakens. These abundance ratios are almost in a steady state,
but that steady state changes slightly as $T$ falls. These patterns show
almost equal values for $Y_3$ because that curve is relatively flat
with time near $t-t_{6000 {\rm K}} = 10^7$ s (Fig. \ref{fig:yi}).
Table \ref{tab:flows} lists our computed reaction flows both in and out of
$\csix$\ at $T = 2031$ K and $T = 1802$ K.
The reactions are specified there in the
compact notation target(in,out)residual. 
We tabulate the flow magnitudes for $\csix$ to aid readers checking our
numerical results. Fig. \ref{fig:cn} and
Table \ref{tab:flows} are made to be studied together.
Note that the abundances of $\ceight$\ are very small:
$Y_8= 10^{-36}$ at $T = 1802$ K.
The isomeric transition from linear to
ringed $\ceight$, for which we estimate a lifetime $\tau = 10$ s,
provides the nucleations for graphite growth.

We call attention to several conclusions to be drawn from Table \ref{tab:flows}.
Firstly, the strongest flows by a wide margin involving $\csix$\ are
\cfivectocsix,
which is very fast ($k = 3 \times 10^{-10} {\rm cm}^3 {\rm s}^{-1}$)
because vibrational excitation of $\csix$
obviates the need for creating a photon \citep{1999Sci...283.1290C},
and its inverse reaction which ejects a C atom. Furthermore, those two flows
are equal to each other to three significant figures, illustrating the near 
steady
state of the abundance pattern. Secondly, thermal dissociation of $\csix$\ is
very much faster than its oxidation, showing the small effect of oxidation
on the abundance pattern. The destroying flows from $\csix$\ to $\cfive$
stand in the approximate ratio
${\rm C}_6(\gamma,{\rm C})/{\rm C_6}({\rm O},{\rm CO}) = 5 \times 10^5$
at $T = 2031$ K and $2 \times 10^4$ at $T = 1802$ K.
Dissociation by thermally excited vibrations dominates oxidation. What we here
label ($\gamma,{\rm C}$) is actually radiationless. Note that oxidation of
$\cenn$ molecules is not faster than C-ejection reactions. This unusual
situation occurs because the C-capture reactions proceed by exciting 
vibrations of the $\csix$ molecule. That residual vibrational energy makes
capture reactions fast rather than slow, but also makes the inverse C-ejection
reactions caused by thermally excited vibrations to be much faster. Detailed
balance gets the ratio right. The smaller value for that ratio at $T=1802$ K
occurs because oxidation maintains its effectiveness as $T$ drops but
thermal disruption does not, being much more temperature sensitive.
For this reason the abundance pattern is flatter and $\csix$\ is approximately
3000 times more abundant at $T=1802$ K than at $T=2031$ K.
It is for that reason that destruction flows in Table \ref{tab:flows}
for $\csix$\ are
larger at the smaller temperature.
The steady state shifts to new ratios as $T$ falls.
Thirdly, calculation of the rates will be illustrated for sake of clarity
by the flow
\csixotococfive.
From Fig. \ref{fig:cn}
one sees that at $T = 2031$ K the abundance $Y_6 = 10^{-33.3}$.
The value of $Y_O = 10^{10} cm^{-3} / 1.1 \times 10^{10} cm^{-3} = 0.909$,
so the flow per atom per
second (e.g., Eq. \ref{eq:dycodt}) is
$dY/dt= Y_6 Y_O n(2031K)k(\csix + {\rm O})$.
Expansion from $T=6000$ K to $T=2031$ K has diluted the total number
density $n$ to $1.1 \times 10^{10}{\rm cm}^{-3}
(2031 {\rm K}/6000 {\rm K})^3 = 4.27 \times 10^8{\rm cm}^{-3}$.
The fast oxidation reaction rate factor is
$k(\csix + {\rm O}) = 3 \times 10^{-10} {\rm cm}^3{\rm s}^{-1}$.
Gathering factors yields approximately $4 \times 10^{-35}$ per atom
per second
in good approximation to the Table \ref{tab:flows}
flow entry $3.61 \times 10^{-35}$ per atom per second.

@@

\item Instead of growing large CO abundance near $Y_{CO}=0.1$ at $T=5500$ K
as in Fig. 11 of \citet{2009ApJ...703..642C}, we find that $Y_{CO}$
builds to a maximum of only $10^{-3}$, which it achieves only slowly
(Fig. \ref{fig:ncoc2}), reaching that maximum only at $T=3500$ K rather
than 5500 K.

@@

\end{enumerate}
We reason that these big differences can be understood if
\citet{2009ApJ...703..642C} had inadvertantly omitted the thermal
dissociation rates of small carbon molecules. Believing that to be the
cause for the discrepancy, we tested that hypothesis by performing our
own trial calculation involving only C, O, CO, $\ctwo$, and $\cthree$,
as they had done,
and omitted the $\tau_\gamma$ destruction terms and the oxidation of $\cthree$.
Figure \ref{fig:no_gamma} displays the result.
The rapid rise of $Y_{CO}$ to about $10^{-2}$ at high temperature is very 
similar to Fig. 11 of \citet{2009ApJ...703..642C}.
Similar also is $Y_2$,
which grows quickly (Fig. \ref{fig:no_gamma}) to $2 \times 10^{-4}$ of $Y_{CO}$,
whereas our Fig. \ref{fig:ncoc2} shows the true value of $Y_{CO}$ to be
only $10^{-8}$ at $T=5500$ K and, considerably later,
$Y_2/Y_{CO} = 10^{-7}$ at their maxima.

With photodissociation turned off, the destruction of $\ctwo$\ occurs primarily
by oxidation, \ctowotococ, whereas production of $\ctwo$ is by
\coctoctwo, the reaction we study in this work.
Those reactions strive to balance, which if achieved would
establish a steady state
ratio $Y_{CO}/Y_2 = 3.5 \times 10^4$. Fig. \ref{fig:no_gamma}
and their Fig. 11 do show
approximately that value, but $Y_2$ declines faster than $Y_{CO}$
because of declining production of $\ctwo$\ as T declines.

@@

\begin{figure}
\plotone{ncoeq}
\caption{
Comparison of the density of CO molecules calculated by the numerical
network (curve) with the expectation $\ncogeq = n_C n_O k_{CO} \tau_\gamma$
for an abundance
$n_{CO}$ in thermal equilibrium (dots) with photons.
Above T=4000K the CO abundance is seen to be in an accurate thermal
equilibrium, but at lower temperature $n_{CO}$ is increasingly smaller than
thermal equilibrium would require. Instead of thermal photons,
the destruction of CO becomes increasingly dominated by
Compton electrons for $T < 3500$ K.
One see in Fig. \ref{fig:nco} that $n_{CO,max}$ occurs near 3500K,
which occurs near $10^7$ s (see Table \ref{tab:quantities}).} 
\label{fig:nco}
\end{figure}

@@

\begin{figure}
\plotone{Yi}
\caption{
The abundance (number per atom) of linear chains $\cenn$\ and of ringed isomer
$\ceightr$. We have scaled each $Y_n$ by the factor stated in the box.}
\label{fig:yi}
\end{figure}

@@

\begin{figure}
\plotone{cn}
\caption{
Shape of $\log10(Y_n)$ vs. n for $\cthree$\ to $\ceight$
at two different temperatures
near 2000K. These shapes can be understood by the relative magnitudes of
flows into and out of $\cenn$.
}
\label{fig:cn}
\end{figure}

@@

\begin{figure}
\plotone{no_gamma}
\caption{
Abundances for network containing only C, O, CO, $\ctwo$, and $\cthree$
when photodissociation of molecules is omitted. Rapid rise of $Y_{CO}$
to $10^{-2}$ near 5500 K and the ratio $Y_{CO}/Y_2$ near $10^4$ are
similar to Fig. 11 of \citet{2009ApJ...703..642C}.
}
\label{fig:no_gamma}
\end{figure}

@@

\begin{table}
\begin{center}
\caption{Values of $\tau_\gamma$(CO) and related quantities at
selected time $t$ and temperature $T$}
\label{tab:quantities}
\begin{tabular}{ccccccc}
\tableline\tableline
$t$ (s) & $\left[t / t_{6000 {\rm K}} \right]^{-3}$ & $T$ (K) & $\tau_\gamma$ (s) & $k_{CO}$ (cm$^{-3}$ s$^{-1}$) & $\ncogeq$ (cm$^{-3}$) \\
\tableline
$5.47 \times 10^6$ &
  1 &
  6000 &
  $4.22 \times 10^{-2}$ &
  $3.13 \times 10^{-17}$ &
  $1.32 \times 10^1$ \\
$5.97 \times 10^6$ &
  0.769 &
  5500 &
  $3.54 \times 10^{-1}$ &
  $2.99 \times 10^{-17}$ &
  $6.27 \times 10^1$ \\
$6.57 \times 10^6$ &
  0.578 &
  5000 &
  $4.46 \times 10^{0}$ &
  $2.83 \times 10^{-17}$ &
  $4.24 \times 10^2$ \\
$7.30 \times 10^6$ &
  0.422 &
  4500 &
  $9.70 \times 10^{1}$ &
  $2.67 \times 10^{-17}$ &
  $4.61 \times 10^3$ \\
$8.21 \times 10^6$ &
  0.296 &
  4000 &
  $4.43 \times 10^{3}$ &
  $2.48 \times 10^{-17}$ &
  $9.67 \times 10^4$ \\
$9.38 \times 10^6$ &
  0.198 &
  3500 &
  $5.86 \times 10^{5}$ &
  $2.28 \times 10^{-17}$ &
  $5.26 \times 10^6$ \\
$1.09 \times 10^7$ &
  0.125 &
  3000 &
  $3.77 \times 10^{8}$ &
  $2.05 \times 10^{-17}$ &
  $1.21 \times 10^9$ \\
\tableline
\end{tabular}
\end{center}
\end{table}

@@

\end{CJK*}
\end{document}
